High-level cognition during story listening is reflected in high-order dynamic correlations in neural activity patterns

### 2021-08-05 paper/main.tex
updated with zenodo doi and update release number

The authors declare that the data supporting the findings of this
study as well as the source data for this paper are available at
\href{https://github.com/ContextLab/timecorr-paper/releases/tag/v0.3}{github.com/ContextLab/timecorr-paper/releases/tag/v0.3}
and has been deposited in the Zenodo database under accession code
(link here).
The raw fMRI data are protected and are not available due to data
privacy laws. The processed fMRI dataset collected by
\cite{SimoEtal16} has been made publicly available \cite{SimoEtal16b} at
\href{http://arks.princeton.edu/ark:/88435/dsp015d86p269k}{arks.princeton.edu/ark:/88435/dsp015d86p269k}.

@@

All of our analysis code may be downloaded from
\href{https://github.com/ContextLab/timecorr-paper/releases/tag/v0.3}{github.com/ContextLab/timecorr-paper/releases/tag/v0.3}. We have also published a companion Python toolbox that may be downloaded from \href{https://timecorr.readthedocs.io}{timecorr.readthedocs.io}.

>>>>

The authors declare that the data supporting the findings of this
study as well as the source data for this paper are available at
\href{https://github.com/ContextLab/timecorr-paper/releases/tag/v0.4}{github.com/ContextLab/timecorr-paper/releases/tag/v0.4}
and has been deposited in the Zenodo database under accession code \href{https://doi.org/10.5281/zenodo.5165253}{https://doi.org/10.5281/zenodo.5165253}.
The raw fMRI data are protected and are not available due to data
privacy laws. The processed fMRI dataset collected by
\cite{SimoEtal16} has been made publicly available \cite{SimoEtal16b} at
\href{http://arks.princeton.edu/ark:/88435/dsp015d86p269k}{arks.princeton.edu/ark:/88435/dsp015d86p269k}.

@@

All of our analysis code may be downloaded from
\href{https://github.com/ContextLab/timecorr-paper/releases/tag/v0.3}{github.com/ContextLab/timecorr-paper/releases/tag/v0.4}. We have also published a companion Python toolbox that may be downloaded from \href{https://timecorr.readthedocs.io}{timecorr.readthedocs.io}.
